% In this file you should put the actual content of the blueprint.
% It will be used both by the web and the print version.
% It should *not* include the \begin{document}
%
% If you want to split the blueprint content into several files then
% the current file can be a simple sequence of \input. Otherwise It
% can start with a \section or \chapter for instance.


%%% GOALS %%%
% Big goal: prove F is finitely generated
% 1. Define F
% 2. Define elements of F
% 3. Tree pairs
% 4. Equivalence on binary trees (caret reduction)
% 5. Equivalence on tree pairs
% 6. Define generators
% 7. Infinite generating set
% 8. Reduction to finite.
% 9. Try doing both cantor set and tree pairs?
% 10. Equivalence trees and clopen subsets of Cantor
% 11. Equivalence tree pairs and cantor 
% 12. Do rational group instead?

\chapter{Preliminaries}

In this section we rehash some basics of the relations between prefix codes, trees and Cantor sets.

\section{Prefix codes}

Let $\{0,1\}$ be a set. Recall that a word over $\{0,1\}$ is a sequence of elements of $\{0,1\}$, the set of all words over $\{0,1\}$
including the empty word is denoted by $\{0,1\}^\ast$. We will write $xy$ for the concatenation of words $x, y\in \{0,1\}^\ast$. We denote the empty word by \(\varepsilon\).
We denote the length of a word \(x\in \{0,1\}^*\) by \(|x|\).
A word $x$ is a \emph{prefix} of a word $y$ if there exists a word $z$ such that $xz = y$. We write $x \preceq y$
to denote that $x$ is a prefix of $y$.
\begin{definition}%
  \label{def:comparable}
 \rocq{Thompson.codes.comparable}
  \rocqok{}
  Let $x, y\in A^\ast$. We say that $x$ and $y$ are \emph{comparable} if $x$ is a prefix of $y$ or vice-versa, i.e.
  $x \preceq y$ or $y \preceq x$ holds. If $x$ and $y$ are not comparable, we say they are \emph{incomparable}.
\end{definition}

\begin{lemma}%
  \label{lem:comparable_symm}
  \uses{def:comparable}
  \rocq{Thompson.codes.comparable_symm}
  \rocqok{}
  Let $x, y\in A^\ast$. Then $x$ and $y$ are comparable if and only if $y$ and $x$ are comparable.
\end{lemma}
\begin{proof}
  \rocqok{}
  The proof follows immediately from the definition, as ``or'' is symmetric.
\end{proof}

An important role in the theory of Thompsons groups is played by prefix codes, which we now define.

\begin{definition}%
  \label{def:prefix_code}
  \uses{def:comparable}
  \rocq{Thompson.codes.prefix_code}
  \rocqok{}
  A prefix code over $\{0,1\}$ is a set of words $P$ over $\{0,1\}$ such that every pair of distinct
  words $w_1, w_2\in P$ are incomparable.
\end{definition}



\begin{definition}\label{def:concat_letter_set}
    Let \(x\in \{0,1\}\) and \(S\subseteq \{0,1\}^*\) be finite. We denote the set \(\makeset{xs}{\(s\in S\)}\) by \(xS\).
\end{definition}

\reinis{Finish this section}


\section{The Cantor set}
The Thompson's groups act faithfully on the Cantor space of all infinite binary sequences. 
This perspective makes some proofs easier so we will go back and forth between the two perspectives.
\begin{definition}\label{def:Cantor_space}
  An \emph{infinite word} over \(\{0,1\}\) is a function \(w:\mathbb{N}\to \{0,1\}\). We denote the set of all such infinite words by \(\{0,1\}^{\mathbb{N}}\).
  This set is viewed as a topological space with the product topology using the discrete topology on \(\{0,1\}\).
  We refer to this topological space as the \emph{Cantor space} and denote it by \(\mathfrak{C}\).
  \luna{presumably rocq has the product topology built in?}
  \reinis{Not built in, but the \texttt{mathcomp-analysis} library has it:
  \url{https://math-comp.github.io/analysis/htmldoc/1_16_0/mathcomp.analysis.topology_theory.function_spaces.html\#prod_topology} - this is the type that the topology is defined on, i.e. the set of points in the space, in this case \texttt{forall i, T i} means that its the set of functions $f: I \rightarrow \bigcup_{i\in I} T_i$ mapping $i\in I$ to an element in $T_i$,
  the actual definition of the topology is here:
  \url{https://math-comp.github.io/analysis/htmldoc/1_16_0/mathcomp.analysis.topology_theory.function_spaces.html\#product_topology_def}, its  going a bit over my head to be honest, but it should be possible to figure out by following the links in the documentation.
  }
  \luna{nice!}
\end{definition}
Recall that an element of \(w\in \{0,1\}^*\) is a finite sequence in the alphabet \(\{0,1\}\). There are many equivalent ways to formally define a finite sequence. For our purposes it will be convenient to view an element \(w\in \{0,1\}^*\) as a function whose domain is \(\{0,1,\ldots, n-1\}\) where \(n\) is the length of \(w\).
\luna{does rocq already have a way of going back and forth between equivalent notions of finite sequence?}
\reinis{Yes, usually lemmas involving \texttt{reflect} prove this (going back and forth between computation and definition), they usually end with a letter ``P'' in Rocq sources (for ``Property''?).}
\reinis{
Rocq has a function \texttt{nth} which returns the $n$-th element of a sequence, and there is a reflection lemma in the
\texttt{mathcomp} library, in the theory of sequences there is the \texttt{nthP} lemma \url{https://math-comp.github.io/htmldoc_2_5_0/mathcomp.boot.seq.html\#nthP}, which essentially
says something like: ``being in a sequence is equivalent to being in the image''.}
\luna{nice!}

\begin{definition}\label{def:concat_fin_inf}
\uses{def:Cantor_space}
    Suppose that \(w\in \{0,1\}^*\) and \(x\in \{0,1\}^{\mathbb{N}}\). We write \(wx\) to denote the map from \(\mathbb{N}\) to \(\{0,1\}\) defined by
    \[(n)wx=\begin{cases}
        (n)w & \text{ if }n<|w|\\
        (n-|w|)x & \text{ if }n\geq |w|.        
    \end{cases}.\]
    More generally. If \(S\subseteq \mathfrak{C}\), then we write \(wS\) for the set \(\makeset{wx}{\(x\in S\)}\).
\end{definition}

\begin{definition}\label{def:cones}
\uses{def:concat_fin_inf}
Suppose that \(w\in \{0,1\}^*\). We define the \emph{cone} of \(w\) to be the set
\(w\mathfrak{C}\).
\end{definition}

Recall that for \(v,w\in \{0,1\}^*\), we write \(w\preceq v\) if \(v\in w\{0,1\}^*\).
Hence the following definition.
\begin{definition}\label{def:finite_prefix_of_cantor}
\uses{def:Cantor_space}
We say that \(w\in \{0,1\}^*\) is a \emph{prefix} of \(x\in \{0,1\}^{\mathbb{N}}\) if \(x\in w\mathfrak{C}\). We write $w \preceq x$
to denote that $w$ is a prefix of $x$.
\end{definition}

\begin{definition}\label{def:restriction_of_infinite_string}
\uses{def:Cantor_space}
If \(x\in \mathfrak{C}\) and \(n\in \mathbb{N}\), then we write \(x|_n\) for the map with domain \(\{0,1, \ldots, n-1\}\) with \((i)x|_n=(i)x\) for all \(i<n\).
\end{definition}
\begin{definition}\label{def:restriction_of_finite_string}
If \(v\in \{0,1\}^*\) and \(n\in \mathbb{N}\) satisfies \(n\leq |v|\), then we write \(v|_n\) for the map with domain \(\{0,1, \ldots, n-1\}\) with \((i)v|_n=(i)v\) for all \(i<n\).
\end{definition}

The following description of cones is often more helpful than the definition.
\begin{lemma}\label{lem:cone_prefixes}
\uses{def:finite_prefix_of_cantor,def:cones,def:restriction_of_infinite_string}
    Suppose that \(w\in \{0,1\}^*\) and \(x\in \mathfrak{C}\). Then \(x\in w\mathfrak{C}\) if and only if \(w=x|_{|w|}\).
\end{lemma}
\begin{proof}
    \((\Leftarrow):\) Suppose that \(w =x|_{|w|}\). Define \(x':\mathbb{N}\to \{0,1\}\) by \((n)x'=(n+|w|)x\).
    As \(wx'\in w\mathfrak{C}\), we need only show that \(wx'=x\). Let \(n\in \mathbb{N}\) be arbitrary. We need only show that \((n)wx'=x\). If \(n<|w|\), then we have \((n)wx'=(n)w=(n)x|_{|w|}=(n)x\) as required.
    If \(n\geq |w|\), then \((n)wx'=(n-|w|)x'=(n-|w|+|w|)x=(n)x\) as required.

    \((\Rightarrow):\) Suppose that \(x\in w\mathfrak{C}\). It follows that there is \(x'\in \mathfrak{C}\) such that \(x=wx'\). In particular, for all \(n<|w|\), we have \((n)x|_{|w|}=(n)x=(n)wx'=(n)w\) as required.
\end{proof}
The same works for finite prefixes.
\begin{lemma}\label{lem:finite_cone_prefixes}
\uses{def:finite_prefix_of_cantor,def:cones, def:restriction_of_finite_string}
    Suppose that \(w,v\in \{0,1\}^*\). Then \(v\in w\{0,1\}^*\) if and only if \(|v|\geq |w|\) and \(w=v|_{|w|}\).
\end{lemma}
\begin{proof}
    \((\Leftarrow):\) Suppose that \(|v|\geq |w|\) and \(w =v|_{|w|}\). Define \(v':\{0,1 ,\ldots |v|-|w|-1\}\to \{0,1\}\) by \((n)v'=(n+|w|)v\).
    As \(wv'\in w\{0,1\}^*\), we need only show that \(wv'=v\). First note that \(|v|=|w|+|v'|=|w|+|v|-|w|=|w|\).
    Let \(n<|v|\) be arbitrary. We need only show that \((n)wv'=v\). If \(n<|w|\), then we have \((n)wv'=(n)w=(n)v|_{|w|}=(n)v\) as required.
    If \(n\geq |w|\), then \((n)wv'=(n-|w|)v'=(n-|w|+|w|)v=(n)v\) as required.

    \((\Rightarrow):\) Suppose that \(v\in w\{0,1\}^*\). It follows that there is \(v'\in \{0,1\}^*\) such that \(v=wv'\).
    We have \(|v|=|w|+|v'|\geq |w|\).
    Moreover, for all \(n<|w|\), we have \((n)v|_{|w|}=(n)v=(n)wv'=(n)w\) as required.
\end{proof}

\begin{lemma}\label{lem:double_restrict}
\uses{lem:cone_prefixes,lem:finite_cone_prefixes}
    Suppose that \(v,w\in \{0,1\}^*\) and \(x\in \mathfrak{C}\) are such that \(w\preceq v\) and \(v\preceq x\). Then \(w\preceq x\).
\end{lemma}
\begin{proof}
By the definition of \(\preceq\) and Lemma~\ref{lem:finite_cone_prefixes}, it follows that \(v|_{|w|}=w\). Similarly, using Lemma~\ref{lem:cone_prefixes}, we have \(x|_{|v|}=v\).
By Lemma~\ref{lem:cone_prefixes} we need to show that \(x|_{|w|}=w\).
This follows as for all \(n<|w|\) we have \((n)x|_{|w|}=(n)x=(n)x|_{|v|}=(n)v=(n)v|_{|w|}=(n)w\).
\end{proof}

\begin{lemma}\label{lem:comp_cone_vs_word}
\uses{def:cones,lem:cone_prefixes,lem:double_restrict}
    If \(v,w\in \{0,1\}^*\), then \(w\preceq v \iff w\mathfrak{C} \supseteq v\mathfrak{C}\).
\end{lemma}
\begin{proof}
\((\Rightarrow):\) Suppose that \(w\preceq v\) and \(x\in \mathfrak{C}\). We show that \(vx\in w\mathfrak{C}\). In other words, we must show that \(w\preceq vx\). As \(w\preceq v\) and \(v \preceq vx\), this follows from Lemma~\ref{lem:double_restrict}.

\((\Leftarrow):\) Suppose that \(v\mathfrak{C} \subseteq w\mathfrak{C}\). We show that \(w\preceq v\). 
Suppose for a contradiction that \(w\) is not a prefix of \(v\). It follows from Lemma~\ref{lem:finite_cone_prefixes} that either \(|w|>|v|\) or (\(|w|\leq |v|\) and \(v|_{|w|}\neq w\)). We consider each case separately.

Case 1: Suppose that \(|w|>|v|\). Let \(x: \mathbb{N}\to \{0,1\}\) be defined by \((n)x=1-(|v|)w\) for all \(n\in \mathbb{N}\). Note that \(vx\in v\mathfrak{C}\). Thus \(vx\in w\mathfrak{C}\).
By Lemma~\ref{lem:cone_prefixes}, it follows that \((vx)|_{|w|}=w\).
In particular, \((|v|)w=(|v|)(vx)|_{|w|}=(|v|)vx=(|v|-|v|)x=1-(|v|)w\). 
This is a contradiction.

Case 2: Suppose that \(|w|\leq |v|\) and \(v|_{|w|}\neq w\). Let \(x:\mathbb{N}\to \{0,1\}\) be defined by \((n)x=0\) for all \(n\in \mathbb{N}\). Then \(vx\in v\mathfrak{C}\).
It follows that \(vx\in w\mathfrak{C}\). 
By Lemma~\ref{lem:cone_prefixes}, it follows that \((vx)|_{|w|}=w\). 
As \((vx)|_{|w|}=v|_{|w|}\), this is a contradiction.
\end{proof}

\begin{lemma}\label{lem:words=cones}
\uses{lem:comp_cone_vs_word}
    If \(v,w\in \{0,1\}^*\), then \(w= v \iff w\mathfrak{C} = v\mathfrak{C}\).
\end{lemma}
\begin{proof}
    This follows from Lemma~\ref{lem:comp_cone_vs_word} since \(\preceq\) and \(\subseteq\) are partial orders.
\end{proof}

\begin{lemma}\label{lem:intersecting_cones}
\uses{lem:cone_prefixes}
If \(v,w\in \{0,1\}^*\) and \(v\mathfrak{C} \cap w\mathfrak{C} \neq \varnothing\), then either \(v\mathfrak{C} \subseteq w\mathfrak{C}\) or \(w\mathfrak{C} \subseteq v\mathfrak{C}\).
\end{lemma}
\begin{proof}
    If \(v\mathfrak{C} \cap w\mathfrak{C} \neq \varnothing\), then there is some \(x\in v\mathfrak{C} \cap w\mathfrak{C}\). 
    In particular \(v\preceq x\) and \(w\preceq x\).
    By Lemma~\ref{lem:cone_prefixes}, it follows that \(x|_{|v|}=v\) and \(x|_{|w|}=w\).
    We either have \(|v|\geq |w|\) or \(|w|\geq |v|\). We consider each case separately.

    Case 1: Suppose that \(|v|\geq |w|\). Then \(v|_{|w|}=(x|_{|v|})|_{|w|}=x|_{|w|}=w\). By Lemma~\ref{lem:finite_cone_prefixes}, it follows that \(w\leq v\). Thus by Lemma~\ref{lem:cone_prefixes}, we have \(v\mathfrak{C} \subseteq w\mathfrak{C}\).

    Case 2: Suppose that \(|w|\geq |v|\). Then \(w|_{|v|}=(x|_{|w|})|_{|v|}=x|_{|v|}=v\). By Lemma~\ref{lem:finite_cone_prefixes}, it follows that \(v\leq w\). Thus by Lemma~\ref{lem:cone_prefixes}, we have \(w\mathfrak{C} \subseteq v\mathfrak{C}\).
\end{proof}

\begin{lemma}\label{lem:incompwords_vs_disjoint_cones}
    \uses{lem:intersecting_cones}
    If \(v,w\in \{0,1\}^*\), then \(v\) and \(w\) are incomparable if and only if \(v\mathfrak{C} \cap w \mathfrak{C} =\varnothing\).
\end{lemma}
\begin{proof}
    \((\Rightarrow):\) We show the contrapositive.
    Suppose that \(v\mathfrak{C} \cap w \mathfrak{C} \neq \varnothing\). By Lemma~\ref{lem:intersecting_cones}, it follows that \(v\mathfrak{C} \subseteq w\mathfrak{C}\) or \(w\mathfrak{C} \subseteq v\mathfrak{C}\). Thus by Lemma~\ref{lem:comp_cone_vs_word}, it follows that either \(w\preceq v\) or \(v\preceq w\).
    So \(v\) and \(w\) are comparable.

    \((\Leftarrow):\) We show the contrapositive. Suppose that \(v\) and \(w\) are comparable. 
    
    Case 1: If \(v\preceq w\), then by Lemma~\ref{lem:comp_cone_vs_word}, we have \(w\mathfrak{C} \subseteq v\mathfrak{C}\). In particular, \(v\mathfrak{C}\cap w\mathfrak{C}=w\mathfrak{C}\neq \varnothing\).

    Case 2: If \(w\preceq v\), then by Lemma~\ref{lem:comp_cone_vs_word}, we have \(v\mathfrak{C} \subseteq w\mathfrak{C}\). In particular, \(w\mathfrak{C}\cap v\mathfrak{C}=v\mathfrak{C}\neq \varnothing\).
\end{proof}

\begin{lemma}\label{lem:prefix_code_disjoint_cones}
\uses{lem:intersecting_cones, def:prefix_code}
If \(P \subseteq \{0,1\}^*\), then \(P\) is a prefix code if and only if the sets \(v\mathfrak{C}\) and \(w\mathfrak{C}\) for \(v,w\in P\) are pairwise disjoint.
\end{lemma}
\begin{proof}
    By Definition~\ref{def:prefix_code}, \(P\) is a prefix code if and only if all the words \(v,w\in P\) are pairwise incomparable. By Lemma~\ref{lem:intersecting_cones}, this is equivalent to saying that the sets \(v\mathfrak{C}\) and \(w\mathfrak{C}\) for \(v,w\in P\) are pairwise disjoint.
\end{proof}


\begin{definition}%
  \label{def:complete_prefix_code}
  \uses{def:prefix_code}
A complete prefix code is a prefix code \(P\) such that for all  $x\in \mathfrak{C}$, there is $p_x\in P$ with \(x\in p_x\mathfrak{C}\).
\end{definition}
\begin{lemma}\label{lem:prefix_code=cone_parition}
  \uses{lem:prefix_code_disjoint_cones, lem:words=cones,def:complete_prefix_code,lem:incompwords_vs_disjoint_cones}
  A subset \(P\subseteq \{0,1\}^*\) is a complete prefix code if and only if \(\makeset{w\mathfrak{C}}{\(w\in P\)}\) is a partition of \(\mathfrak{C}\).
\end{lemma}
\begin{proof}
    \((\Rightarrow):\) By Lemma~\ref{lem:prefix_code_disjoint_cones}, the members of the set \(\makeset{w\mathfrak{C}}{\(w\in P\)}\) are pairwise disjoint.
    Let \(x:\mathbb{N}\to \{0,1\}\) be defined by \((n)x=0\) for all \(n\in \mathbb{N}\).
    Note that for all \(w\in P\), we have \(wx\in w\mathfrak{C}\). Thus \(\makeset{w\mathfrak{C}}{\(w\in P\)}\) does not contain it empty set.
    It remains to check that the members of \(\makeset{w\mathfrak{C}}{\(w\in P\)}\) cover \(\mathfrak{C}\). This follows from the definition of a complete prefix code (Definition~\ref{def:complete_prefix_code}).

    \((\Leftarrow):\) As the members of \(\makeset{w\mathfrak{C}}{\(w\in P\)}\) cover \(\mathfrak{C}\), we need only check that \(P\) is a prefix code.
    Let \(p,q\in P\) be such that \(p\neq q\).
    We must show that \(p\) and \(q\) are incomparable.
    We have \(p\mathfrak{C},q\mathfrak{C}\in \makeset{w\mathfrak{C}}{\(w\in P\)}\).
    So either \(p\mathfrak{C}=q\mathfrak{C}\) or \(p\mathfrak{C}\cap q\mathfrak{C}=\varnothing\). We consider these cases separately.

    Case 1: Suppose that \(p\mathfrak{C}=q\mathfrak{C}\). Then by Lemma~\ref{lem:words=cones}, it follows that \(p=q\). This is a contradiction.

    Case 2: Suppose that \(p\mathfrak{C}\cap q\mathfrak{C}=\varnothing\). Then Lemma~\ref{lem:incompwords_vs_disjoint_cones} implies that \(p\) and \(q\) are incomparable as required.
\end{proof}

\begin{lemma}\label{lem:finite_complete_prefix_codes}
\uses{lem:prefix_code=cone_parition,lem:words=cones}
    All complete prefix codes are finite.
\end{lemma}
\begin{proof}
Let \(P\) be a complete prefix code.
By Lemma~\ref{lem:prefix_code=cone_parition}, the set \(\makeset{w\mathfrak{C}}{\(w\in P\)}\) is a partition of \(\mathfrak{C}\).
As the elements of this partition are open.
\luna{the proof that they're open depends on how the product topology is handled in rocq}
\reinis{I would assume that this might already be implictly proved somewhere in the \texttt{mathcomp-analysis} library. They have the Cantor space defined in \url{https://math-comp.github.io/analysis/htmldoc/1_16_0/mathcomp.analysis.cantor.html}.}
By Tychonoff's Theorem, the topological space \(\mathfrak{C}\) is compact.
\luna{I'm just guessing that rocq has Tychonoff's Theorem.}
\reinis{Oui, it seems they do in \texttt{mathcomp-analysis}:
\url{https://math-comp.github.io/analysis/htmldoc/1_16_0/mathcomp.analysis.topology_theory.function_spaces.html\#tychonoff}}
\luna{nice!}
As \(\makeset{w\mathfrak{C}}{\(w\in P\)}\) is an open cover of \(\mathfrak{C}\) it has a finite subcover. 
As this set is a partition, no strict subcover is still a cover. It follows that the set \(\makeset{w\mathfrak{C}}{\(w\in P\)}\) is finite.
By Lemma~\ref{lem:words=cones}, the map \(w\mapsto w\mathfrak{C}\) from \(P\) to this cover is an injective map.
As there is an injective map from \(P\) to a finite set, it follows that \(P\) is finite.
\luna{assuming rocq has a thing for this}
\reinis{Yes, its probably in the base \texttt{mathcomp} library, in the \texttt{fintype} theory:
\url{https://math-comp.github.io/htmldoc_2_5_0/mathcomp.boot.fintype.html}.}
\reinis{I think we can probably prove this a bit more combinatorially, however, if we change the definition of complete code to say something like ``A code is complete if the associated tree has no missing edges''}
\reinis{Alternatively we could take the definition to be something like ``a prefix code is complete if it either consists of only the empty word, or alternatively, for every word $w$ of length at least $1$ in the code, if we can write $w = w^\prime a$, then there exist words $w_0, w_1$ in the code such that $w^\prime 0$ is a prefix of $w_0$ and $w^\prime 1$ is a prefix of $w_1$.}
\reinis{We then only need to prove the partition of $\mathfrak{C}$ lemma (which follows through essentially the same) and dont need this lemma at all.}
\luna{I agree with all of this. I think its likely we can work around this lemma but not confident depending on what we end up doing.
I'm not sure where rocq falls on the boundary of coding and maths. Like in maths its bad to make a paper longer by proving things you don't need. But in software its (arguably) good to add more features even if they aren't guaranteed to be used. In maths there is cost to the reader when extra stuff is added. This is not the same with users of software. Although software does need to be maintained and stuff. Do you have thoughts on these thoughts?}
\end{proof}
\section{Trees}

We wish to view elements of Thompson's group \(V\) as equivalence classes of tree pairs. We must establish some terminology about binary trees in order to do this.
\begin{definition}%
  \label{def:rooted_binary_tree}
\uses{def:prefix_code,def:concat_letter_set}
 A finite rooted binary tree \(T\) is one of:
 \begin{itemize}
     \item \(\{\varepsilon\}\);
     \item a set of the form \(0T_0 \cup 1T_1 \cup \{\varepsilon\}\) where \(T_0\) and \(T_1\) are finite rooted binary trees.
 \end{itemize}
\end{definition}

\begin{definition}%
  \label{def:leaf_of_a_tree}
\uses{def:rooted_binary_tree}
If \(T\) is a finite rooted binary tree, then a leaf of \(T\) is one of
\begin{itemize}
    \item \(\varepsilon\) if \(T=\{\varepsilon\}\);
    \item \(0l\) if \(T=0T_0 \cup T_1 \cup \{\varepsilon\}\) and \(l\) is a leaf of \(T_0\);
    \item \(1l\) if \(T=0T_0 \cup T_1 \cup \{\varepsilon\}\) and \(l\) is a leaf of \(T_1\).
\end{itemize}
\end{definition}

\begin{definition}%
  \label{def:leaf_set_of_a_tree}
\uses{def:leaf_of_a_tree}
If \(T\) is a finite rooted binary tree, then \(\mathcal{L}(T):=\makeset{t\in T}{\(t\) is a leaf of \(T\)}\).
\end{definition}

\begin{definition}%
  \label{def:tree_pair}
\uses{def:leaf_set_of_a_tree}
A tree pair is a triple \((T_1,T_2,\phi)\) where \(T_1\) and \(T_2\) are finite rooted binary trees and \(\phi:\mathcal{L}(T_1)\to \mathcal{L}(T_2)\) is a bijection.
\end{definition}

\begin{definition}\label{def:tree_elementary_expansions}
    \uses{def:rooted_binary_tree}
    If \(T\) is a rooted binary tree and \(l\) is a leaf of \(T\), then we define the \emph{elementary expansion} \(T'\) of \(T\) at \(l\) to be the set:
    \begin{itemize}
        \item \(\{\varepsilon,0,1\}\) if \(l=\varepsilon\);
        \item \(0T_0'\cup 1 T_1 \cup \{\varepsilon\}\) if \(T=0T_0 \cup 1T_1 \cup \{\varepsilon\}\), \(l=0l'\) for a leaf \(l'\) of \(T_0\), and \(T_0'\) is the elementary expansion of \(T_0\) at \(l'\);
  \item \(0T_0\cup 1 T_1' \cup \{\varepsilon\}\) if \(T=0T_0 \cup 1T_1 \cup \{\varepsilon\}\), \(l=1l'\) for a leaf \(l'\) of \(T_1\), and \(T_1'\) is the elementary expansion of \(T_1\) at \(l'\).
    \end{itemize}
\end{definition}

\begin{lemma}\label{lem:tree_elementary_expansion_is_tree}
    \uses{def:tree_elementary_expansions}
    If \(T\) is a finite rooted binary tree and \(l\) is a leaf of \(T\), then the elementary expansion \(T'\) of \(T\) at \(l\) is also a finite rooted binary tree.
 \end{lemma}
 \begin{proof}
 We proceed by recursion:
 \luna{Note sure how to write this properly but pretty sure rocq can accept proofs like this}
 \reinis{This is just a proof by induction I think. Rocq can do those.}
 \reinis{But I think in general this is a bit too set-theoretic of a definition!}
 \reinis{The way we define trees in Rocq is a bit closer (if not the same) as the J´onsson-Tarski variety approach. I.e. the set of binary trees as we would define in Rocq using the \texttt{Inductive} keyword is essentially the free algebra \texttt{binary\_tree} generated by a single element \texttt{Empty} together with a single (non-associative!) binary operator
 $\texttt{Node}: \texttt{binary\_tree}\times \texttt{binary\_tree}\rightarrow \texttt{binary\_tree}$.
 The interpretation is that \texttt{Empty} is the empty tree, and the \texttt{Node} function takes two trees and produces a new tree by creates a new node and attaching the two trees as the right and left subtree.
 }
 \luna{This sounds cool! This is the same as the J´onsson-Tarski definition except in J´onsson-Tarski there are also two unary operations which undo the binary. I actually prefer this viewpoint. However without the set theoretic definition with finite words its unclear how to relate this to the cantor set. The usual way to relate the free J´onsson-Tarski algebra to the cantor set is by using the unary operations and noting that each endomorphism of the free J´onsson-Tarski algebra is determined by its birestriction to the set of elements reachable from the free generator using the unarys. The elements of the cantor set appear as the ``boundary" of the infintie binary tree defined by the unarys.
 It seems to me that the two most reasonable options are to either use an actual J´onsson-Tarski algebra (which I'm a big fan of and might even be more rocq friendly) or to use the definition of trees I use here. I'm of course open to counter suggestions though.}
 \reinis{Yes we can do this! Essentially we take the free algebra with a binary operation generated by a single element and then define the two unaries as partial functions (we need to do this as they can't be defined on the singleton tree, i.e. just a root with no children), and Bobs your uncle.}
 \luna{In the usual J´onsson-Tarski framework we are allowed to apply the unarys to the singleton tree as well. Is this bad?}
 \reinis{What do you get as a result? Is it defined? or is it just the free thing, like if we call the unaries \texttt{Left} and \texttt{Right},
 is something like $\texttt{Left}(\texttt{Right}(\texttt{Empty}))$ allowed,
 and is it just a new unique element with no meaning? But then what happens if I apply the binary operation to it? Like
$\texttt{Node}(\texttt{Left}(\texttt{Right}(\texttt{Empty})), \texttt{Empty})$?}
 \reinis{Am I correct in assuming the unaries essentially just take us to the left and right subtree respectively in a normal tree?}
 \luna{all your assumptions are correct. This is indeed a well defined element $\texttt{Node}(\texttt{Left}(\texttt{Right}(\texttt{Empty})), \texttt{Empty})$. We do add the laws that $\texttt{Node}(\texttt{Left}(thing), \texttt{Right}(thing)) = thing$ and $\texttt{Right}(\texttt{Node}(thing1, thing2))=thing2$ and $\texttt{Left}(\texttt{Node}(thing1, thing2))=thing1$}
\reinis{Is there any semantic meaning to $\texttt{Left}(\texttt{Right}(\texttt{Empty}))$? I.e. for $\texttt{Node}$ the meaning is: ``build a bigger tree taking two smaller subtrees as left and right child''.
When applied to a $\texttt{Node}$, the semantic of $\texttt{Left}$ is ``take the left child''. But what is the meaning when we apply $\texttt{Left}$ to $\texttt{Empty}$? If this is meaningless and just a quirk of the theory, then
do we lose much by adding in a constraint that says its undefined?}
\luna{the way I think of it is that the stuff make-able from \(\texttt{Empty}\) using \(\texttt{Left}\) and \(\texttt{Right}\) is a copy of the free monoid on two letters and the elements of the algebra are trees whose leaves are labelled by elements of this free monoid. If we remove the unarys I think some of the theory will be significantly more complicated. In particular in this framefork $V$ is literally just the automorphism group of this thing, if we restrict we need to be way more careful}
\reinis{Ok gotcha, this makes sense. We can 100\% make such an algebra in Rocq. We would only need to implement a normalization procedure to take care of the extra laws $\texttt{Node}(\texttt{Left}(thing), \texttt{Right}(thing)) = thing$ and $\texttt{Right}(\texttt{Node}(thing1, thing2))=thing2$ and $\texttt{Left}(\texttt{Node}(thing1, thing2))=thing1$.}
\luna{sounds good. the word problem is easy to solve}
\reinis{Lets do that then, it seems you have a pretty good grasp of these algebras already, so please go ahead whenever you want. I am just not a fan of set theory :D}

\luna{thanks :). lol. }

 Case 1: Suppose that \(T'=\{\varepsilon,0,1\}\). 
 Then \(T'=0\{\varepsilon\} \cup 1\{\varepsilon\} \cup \{\varepsilon\}\). As \(\{\varepsilon\}\) is a finite rooted binary tree, it follows that \(T'\) is a finite rooted binary tree.

 Case 2: Suppose that \(T'= 0T_0'\cup 1 T_1 \cup \{\varepsilon\}\), \(T=0T_0 \cup 1T_1 \cup \{\varepsilon\}\), \(l=0l'\) for a leaf \(l'\) of \(T_0\), and \(T_0'\) is the elementary expansion of \(T_0\) at \(l'\). By recursion, \(T_0'\) is a finite rooted binary tree. Thus \(T'\) is also a finite rooted binary tree.
 
 Case 3: Suppose that \(T'= 0T_0\cup 1 T_1' \cup \{\varepsilon\}\), \(T=0T_0 \cup 1T_1 \cup \{\varepsilon\}\), \(l=1l'\) for a leaf \(l'\) of \(T_1\), and \(T_1'\) is the elementary expansion of \(T_1\) at \(l'\). By recursion, \(T_1'\) is a finite rooted binary tree. Thus \(T'\) is also a finite rooted binary tree.
 \end{proof}

\begin{lemma}\label{lem:leaves_of_elementary_expanion}
    \uses{lem:tree_elementary_expansion_is_tree}
    If \(T\) is a finite rooted binary tree, \(l\) is a leaf of \(T\) and \(T'\) is the elementary expansion of \(T\) at \(l\), then \(\mathcal{L}(T')=(\mathcal{L}(T)\backslash \{l\})\cup \{l0,l1\}\). Moreover this is a disjoint union.
 \end{lemma}
 \begin{proof}
 Note that Lemma~\ref{lem:tree_elementary_expansion_is_tree} is required for the statement to be well-defined.
 \luna{note sure how to say that properly}
 We proceed by recursion.
     There are three cases for \(T'\).

     Case 1: Suppose that \(T'= \{\varepsilon\}\) and \(l=\varepsilon\). As \(T'\) is an elementary expansion of \(T\), it follows (by examining each case) that \(T'\) contains a word beginning with a \(0\). This is a contradiction.

     Case 2: Suppose that \(T'= 0T_0'\cup 1 T_1 \cup \{\varepsilon\}\), \(T=0T_0 \cup 1T_1 \cup \{\varepsilon\}\), \(l=0l'\) for a leaf \(l'\) of \(T_0\), and \(T_0'\) is the elementary expansion of \(T_0\) at \(l'\).  By recursion, \(\mathcal{L}(T_0')\) is equal to the disjoint union \(\mathcal{L}(T_0)\backslash \{l'\})\cup \{l'0,l'1\}\). By Definition~\ref{def:leaf_of_a_tree}, it follows that
     \(\mathcal{L}(T')= 0(\mathcal{L}(T_0)\backslash \{l'\})\cup \{l'0,l'1\})\cup 1\mathcal{L}(T_1)\) and \(\mathcal{L}(T)= 0\mathcal{L}(T_0)\cup 1\mathcal{L}(T_1)\).
     As the first letter of \(l\) is a \(0\), it follows that \(l\in 0\mathcal{L}(T_0)\).
     Thus we need only show that 
     \[0(\mathcal{L}(T_0)\backslash \{l'\})\cup \{l'0,l'1\})= (0\mathcal{L}(T_0)\backslash \{l\})\cup \{l0,l1\}.\]
     \luna{dont know how to reference injectivity of prepending letters}
     \reinis{we get this for free, can just assume without proof. Essentially it is just a consequence of freeness of the set of words.}
     As prepending a \(0\) is injective, it follows that 
     \[0(\mathcal{L}(T_0)\backslash \{l'\})\cup \{l'0,l'1\})=0\mathcal{L}(T_0)\backslash \{0l'\})\cup \{0l'0,0l'1\}\]
     and this union is still disjoint.
     As \(l=0l'\), it follows that this set is equal to \((0\mathcal{L}(T_0)\backslash \{l\})\cup \{l0,l1\}\) as required.
    
 
 Case 3: Symmetric argument to Case 2.

     
 \end{proof}



\begin{lemma}\label{lem:tree_to_codes}
\uses{def:leaf_of_a_tree,def:complete_prefix_code,lem:cone_prefixes}
    If \(T\) is a finite rooted binary tree, then \(\mathcal{L}(T)\) is a complete prefix code.
\end{lemma}
\begin{proof}
    We proceed recursively.

    If \(T=\{\varepsilon\}\), then \(\mathcal{L}(T)=\{\varepsilon\}\). As \(\mathcal{L}(T)\) has only one element, it has no pair of incomparable elements. Thus \(\mathcal{L}(T)\) is a prefix code.
    As \(\varepsilon \preceq x\) for all \(x\in \mathfrak{C}\), it follows that \(\mathcal{L}(T)\) is a complete prefix code.

    Next suppose that \(T=0T_0 \cup 1T_1 \cup \{\varepsilon\}\) for some finite rooted binary trees \(T_0\) and \(T_1\). By recursion, the sets \(\mathcal{L}(T_0)\) and \(\mathcal{L}(T_1)\) are complete prefix codes.
    Moreover, by Definition~\ref{def:leaf_of_a_tree}. We have \(\mathcal{L}(T)=0\mathcal{L}(T_0)\cup 1\mathcal{L}(T_1)\). No word in \(0\mathcal{L}(T_0)\) is comparable with any word of \(1\mathcal{L}(T_1)\) as they have distinct first letters. Moreover the elements of \(\mathcal{L}(T_0)\) being incomparable implies that the elements of \(0\mathcal{L}(T_0)\) are incomparable.
    \luna{todo add reference to reinis's rocq lemma for this}
    Similarly, the elements of \(1\mathcal{L}(T_1)\) are incomparable. Thus \(\mathcal{L}(T)\) is a prefix code.
    Let \(x\in \mathfrak{C}\). 
    There are two cases.

    Case 1: Suppose that \((0)x=0\). It follows from Lemma~\ref{lem:cone_prefixes}, that \(x=0x'\) for some \(x'\in \mathfrak{C}\). There is some \(p\in \mathcal{L}(T_0)\) with \(p\leq x'\). It follows that \(0p \leq x\).

    Case 2: \((0)x=1\). It follows from Lemma~\ref{lem:cone_prefixes}, that \(x=1x'\) for some \(x'\in \mathfrak{C}\). There is some \(p\in \mathcal{L}(T_1)\) with \(p\leq x'\). It follows that \(1p \leq x\).
\end{proof}

\begin{lemma}\label{lem:codes_to_trees}
\uses{def:leaf_of_a_tree,def:complete_prefix_code, lem:finite_complete_prefix_codes}
   If \(P\) is a complete prefix code, then there is a finite rooted binary tree \(T\) with \(\mathcal{L}(T)=P\).
\end{lemma}
\begin{proof}
    Suppose that \(P\) is a complete prefix code.
    By Lemma~\ref{lem:finite_complete_prefix_codes}, \(P\) is a finite set.
    We proceed by induction on the length of the longest element of \(P\).

    Base case: Suppose that \(w\in P\) has maximal length and \(|w|=0\). 
    It follows that \(w=\varepsilon\). As \(P\) is a prefix code, it follows that \(P=\{\varepsilon\}\).
    In particular \(P=\mathcal{L}(T)\) where \(T=\{\varepsilon\}\).

    Inductive hypothesis: Suppose that \(n\in \mathbb{N}\) and for all complete prefix codes \(P\) all of whose words have length at most \(n\), there is a finite rooted binary tree with \(P=\mathcal{L}(T)\).

    Inductive step: Suppose that \(P\) is a complete prefix code and the maximum length of an element of \(P\) is \(n+1\).
    Let \(P_0= P\cap 0\{0,1\}^*\) and  \(P_1= P\cap 1\{0,1\}^*\). 
    For all \(x\in 1 \mathfrak{C}\), there is a prefix of \(x\) belonging to \(P\). 
    As \(P\) is a prefix code and contains a word of positive length, it follows that \(\varepsilon \not\in P\).
    It follows that for all \(x\in 1 \mathfrak{C}\), there is a prefix of \(x\) belonging to \(P_1\).
    Similarly for all \(x\in 0 \mathfrak{C}\), there is a prefix of \(x\) belonging to \(P_0\).
    Let \(P_0'\) be the set obtained from \(P_0\) by removing the first letter of every word. 
    By reinis's thing, the set \(P_0\) is a prefix code. Moreover the elements of \(P_0\) have length at most \(n\).
    As for all \(x\in 0 \mathfrak{C}\), there is a prefix of \(x\) belonging to \(P_0\). Thus \(P_0'\) is a complete prefix code.
    Define a complete prefix code \(P_1'\) similarly.
    By the inductive hypothesis, there are finite rooted binary trees \(T_0\) and \(T_1\) such that
    \[P_0'=\mathcal{L}(T_0)\text{ and }P_1'=\mathcal{L}(T_1).\]
    Let \(T=0T_0\cup 1T_1 \cup \{\varepsilon\}\). Note that by Definition~\ref{def:rooted_binary_tree}, it follows that \(T\) is a finite rooted binary tree.
    Moreover, by Definition~\ref{def:leaf_of_a_tree}, it follows that \(\mathcal{L}(T)=0\mathcal{L}(T_0)\cup 1\mathcal{L}(T_1)=P_0\cup P_1=P\) as required.
\end{proof}

\begin{theorem}\label{thm:tree=complete_prefix_code}
\uses{lem:tree_to_codes,lem:codes_to_trees}
    A subset \(P\subseteq \{0,1\}^*\) is a complete prefix code if and only if it is the set of leaves of a finite rooted binary tree.
\end{theorem}
\begin{proof}
    \((\Rightarrow):\) Lemma~\ref{lem:codes_to_trees}.

    \((\Leftarrow):\) Lemma~\ref{lem:tree_to_codes}.
\end{proof} 


\begin{definition}\label{def:tree_pair_elementary_expansions}
\uses{def:tree_pair,lem:tree_elementary_expansion_is_tree}
If \((T_1,T_2,\phi)\) is a tree pair and \(l\) is a leaf of \(T_1\), then the \emph{elementary expansion} of \(T_1\) at \(l\) is the tree pair \((T_1',T_2',\phi')\) where 
\begin{itemize}
    \item \(T_1'\) is the elementary expansion of \(T_1\) at \(l\);
    \item \(T_2'\) is the elementary expansion of \(T_1\) at \((l)\phi\);
    \item \(\phi':\mathcal{L}(T_1')\to \mathcal{L}(T_2')\) is defined by
    \[(w)\phi':=\begin{cases}
        (w)\phi & \text{ if }w\text{ is a leaf of }T_1\\
        (l)\phi 0 & \text{ if }w=l0\\
        (l)\phi 1 & \text{ if }w=l1.
    \end{cases}\]
    \luna{The argument that these cases are exhaustive (and \(\phi\) is a bijection) is essentially Lemma~\ref{lem:leaves_of_elementary_expanion}. Not sure how to discuss definitions which require proofs to be of the correct type.}
    \reinis{Usually this indicates that there is a way of defining this function recursively (inductively). Alternatively, we can define it as a partial function and then prove a lemma its total.}
\end{itemize}
\end{definition}


\begin{definition}\label{def:prefix_cantor_to_cantor}
\uses{def:complete_prefix_code,def:concat_fin_inf}
For each complete prefix code \(P\), we define a map \(\phi_P:P\times \mathfrak{C}\to \mathfrak{C}\) by \((p,x)\phi_P=px\).
\end{definition}

\begin{lemma}\label{def:cantor_to_prefix_code_cantor}
\uses{def:prefix_cantor_to_cantor,lem:prefix_code=cone_parition,lem:words=cones}
  If \(P\) is a complete prefix code, then there is a unique map \(\phi_P^{-1}:\mathfrak{C}\to P\times \mathfrak{C}\) such that \(\phi_P^{-1}\phi_P\) and \(\phi_P\phi_P^{-1}\) are the identity functions.
\end{lemma}
\begin{proof}
    We need only show that \(\phi_P\) is a bijection.

    Injective: Suppose that \((p,x)\phi_P=(p',x')\phi_P\). It follows that \(px=p'x'\). In particular, \(p\mathfrak{C}\cap p'\mathfrak{C}\neq \varnothing\).
    By Lemma~\ref{lem:prefix_code=cone_parition}, it follows that \(p\mathfrak{C}= p'\mathfrak{C}\). 
    Thus by \cref{lem:words=cones}, we have \(p=p'\).
    For all \(n\in \mathbb{N}\), we have \((n)x=(n+|p|)px=(n+|p|)p'x'=(n+|p|)px'=(n)x'\). Thus \(x=x'\) as well. It follows that \((p,x)=(p',x')\).

    Surjective: Let \(x\in \mathfrak{C}\). It follows from \cref{def:complete_prefix_code} that there is \(p_x\in P\) with \(x\in p_x\mathfrak{C}\). So there is \(x'\in \mathfrak{C}\) with \(x=p_xx'\). In particular, \(x=(p_x,x')\phi_P\).
\end{proof}

\begin{definition}\label{def:direct_sum_of_functions}
    Suppose that \(A\), \(B\), \(C\) and \(D\) are sets. 
    Suppose further that \(f_{A,B}:A\to B\) and \(f_{C,D}:C\to D\) are functions.
    We write \(f_{A,B}\oplus f_{C,D}\) for the function from \(A\times C\) to \(B\times D\) defined by \((a,c)\mapsto ((a)f_{A,B},(c)f_{C,D})\).
\end{definition}

\begin{definition}\label{def:tree_pair_to_prefix_replacement}
\uses{def:cantor_to_prefix_code_cantor,def:direct_sum_of_functions}
Suppose that \(P=(T_1,T_2,\phi)\) is a tree pair. We define a \(f_P:\mathfrak{C}\to \mathfrak{C}\) to be the function
\(f_P = \phi_{\mathcal{L}(T_1)}^{-1} \circ (\phi \oplus \operatorname{id}_{\mathfrak{C}})\circ \phi_{\mathcal{L}(T_2)}.\)
\end{definition}

\begin{lemma}\label{lem:expansions_are_safe}
\uses{def:tree_pair_to_prefix_replacement,def:tree_pair_elementary_expansions}
Suppose that \(P=(T_1,T_2,\phi)\) is a tree pair, \(l\) is a leaf of \(T_1\) and \(P'=(T_1',T_2',\phi')\) is the expansion of \(P\) at \(L\).
Then \(f_{P}=f_{P'}\).
\end{lemma}
\begin{proof}
Let \(x\in \mathfrak{C}\).
We must show that \((x)f_P=(x)f_{P'}\).
By Theorem~\ref{thm:tree=complete_prefix_code}, the set \(\mathcal{L}(T_1')\) is a complete prefix code.
Thus by Lemma~\ref{lem:leaves_of_elementary_expanion}, it follows that \((\mathcal{L}(T)\backslash \{l\})\cup \{l0,l1\}\) is a complete prefix code (and this union is disjoint).
So by Lemma~\ref{lem:prefix_code=cone_parition}, there is a unique \(p\in (\mathcal{L}(T)\backslash \{l\})\cup \{l0,l1\}\) with \(x\in p\mathfrak{C}\). Let \(x'\in \mathfrak{C}\) be such that \(x=px'\).
We proceed by cases.

Case 1: Suppose that \(p\in \mathcal{L}(T)\backslash \{l\}\). It follows that
\begin{align*}
    (x)f_P&=(px')\phi_{\mathcal{L}(T_1)}^{-1} \circ (\phi \oplus \operatorname{id}_{\mathfrak{C}})\circ \phi_{\mathcal{L}(T_2)}\\
    &= (p,x')(\phi \oplus \operatorname{id}_{\mathfrak{C}})\circ \phi_{\mathcal{L}(T_2)}\\
    &= ((p)\phi,x') \phi_{\mathcal{L}(T_2)}\\
    &= (p)\phi \cdot x' 
\end{align*}
As \(p\in \mathcal{L}(T')\) as well and \((p)\phi'=(p)\phi\) by Definition~\ref{def:tree_pair_elementary_expansions}, it follows that similarly
\begin{align*}
    (x)f_{P'}&=(px')\phi_{\mathcal{L}(T_1')}^{-1} \circ (\phi' \oplus \operatorname{id}_{\mathfrak{C}})\circ \phi_{\mathcal{L}(T_2')}\\
    &= (p,x')(\phi' \oplus \operatorname{id}_{\mathfrak{C}})\circ \phi_{\mathcal{L}(T_2')}\\
    &= ((p)\phi',x') \phi_{\mathcal{L}(T_2')}\\
    &= (p)\phi' \cdot x'\\
    &= (p)\phi \cdot x'.
\end{align*}
So \((x)f_P=(x)f_{P'}\) as required.


Case 2: Suppose that \(p=l0\).
It follows that
\begin{align*}
    (x)f_P&=(l0x')\phi_{\mathcal{L}(T_1)}^{-1} \circ (\phi \oplus \operatorname{id}_{\mathfrak{C}})\circ \phi_{\mathcal{L}(T_2)}\\
    &= (l,0x')(\phi \oplus \operatorname{id}_{\mathfrak{C}})\circ \phi_{\mathcal{L}(T_2)}\\
    &= ((l)\phi,0x') \phi_{\mathcal{L}(T_2)}\\
    &= (l)\phi \cdot 0x' .
\end{align*}
As \(l0\in \mathcal{L}(T')\)  and \((l0)\phi'=(l)\phi 0\) by Definition~\ref{def:tree_pair_elementary_expansions}, it follows that similarly
\begin{align*}
    (x)f_{P'}&=(l0x')\phi_{\mathcal{L}(T_1')}^{-1} \circ (\phi' \oplus \operatorname{id}_{\mathfrak{C}})\circ \phi_{\mathcal{L}(T_2')}\\
    &= (l0,x')(\phi' \oplus \operatorname{id}_{\mathfrak{C}})\circ \phi_{\mathcal{L}(T_2')}\\
    &= ((l0)\phi',x') \phi_{\mathcal{L}(T_2')}\\
    &= (l0)\phi' \cdot x'\\
    &= (l)\phi  0\cdot x'\\
    &= (l)\phi\cdot  0 x'.
\end{align*}
So \((x)f_P=(x)f_{P'}\) as required.

Case 3: Suppose that \(p=l1\). Similar to Case 2.
\end{proof}

\begin{definition}\label{def:tree_expansions}
\uses{lem:leaves_of_elementary_expanion}
    We say that a tree \(T'\) is an \emph{expansion} of a tree \(T\) if there is a finite sequence of trees \(T=T_0, T_1,\ldots, T_k= T'\) where \(T_{i+1}\) is an elementary expansion of \(T_i\) for all \(i<k\).
\end{definition}

\begin{lemma}\label{lem:common_tree_expansions}
\uses{def:tree_expansions}
Suppose that \(T\) and \(U\) are finite rooted binary trees.
Then there are expansions \(T'\) and \(U'\) of \(T\) and \(U\) respectively such that \(T'=U'\)
\end{lemma}
\begin{proof}
    \luna{todo finish}
\end{proof}

\begin{definition}\label{def:tree_pair_expansions}
\uses{def:tree_pair_elementary_expansions}
    We say that a tree pair \(P'\) is an \emph{expansion} of a tree pair \(P\) if there is a finite sequence of tree pairs \(P=P_0, P_1,\ldots, P_k= P'\) where \(P_{i+1}\) is an elementary expansion of \(P_i\) for all \(i<k\).
\end{definition}



\begin{lemma}\label{lem:map_eqiv_to_expansion_equiv}
\uses{def:tree_pair_to_prefix_replacement,lem:common_tree_expansions}
    Suppose that \(P\) and \(Q\) are tree pairs such that \(f_P=f_Q\).
    There there are expansions \(P'\) and \(Q'\) of \(P\) and \(Q\) respectively such that \(P'=Q'\).
\end{lemma}
\begin{proof}
    \luna{todo finish}
\end{proof}

\begin{definition}\label{lem:tree_pair_equivalence}
\uses{def:tree_pair_expansions}
    We say that two tree pairs \(P\) and \(Q\) are \emph{equivalent} if they have a common expansion.
    We denote this by \(P\sim Q\).
\end{definition}
\begin{theorem}\label{thm:Vtree_Vcant_bijection}
\uses{lem:tree_pair_equivalence,lem:map_eqiv_to_expansion_equiv,lem:expansions_are_safe}
    If \(P\) and \(Q\) are tree pairs, then \(P\sim Q\) if and only if \(f_P=f_Q\).
\end{theorem}
\begin{proof}
    \luna{todo finish}
\end{proof}
\begin{corollary}\label{cor:tree_equiv_is_equiv}
\uses{thm:Vtree_Vcant_bijection}
The relation \(\sim\) on tree pairs is an equivalence relation.
\end{corollary}

\begin{lemma}\label{lem:cat_comp}
\uses{def:tree_pair_to_prefix_replacement}
If \((T_1,T_2,\phi)\) and \((U_1,U_2,\psi)\) are tree pairs with \(T_2=U_2\), then \((T_1,U_2,\phi \psi)\) is a tree pair and
\[f_{(T_1,T_2,\phi)}f_{(U_1,U_2,\psi)}=f_{(T_1,U_2,\phi \psi)}.\]
\end{lemma}
\begin{proof}
    \luna{todo prove}
\end{proof}
\begin{lemma}\label{lem:compable_expansion}
\uses{lem:common_tree_expansions,def:tree_pair_expansions}
If \(P\) and \(Q\) are tree pairs then there are expansions \(P'\) and \(Q'\) of \(P\) and \(Q\) respectively such that the second tree of \(P'\) is equal to the first tree of \(Q\).
\end{lemma}
\begin{proof}
    \luna{todo prove}
\end{proof}

\begin{lemma}\label{lem:V_is_semigroup}
\uses{lem:compable_expansion}
    If \(P\) and \(Q\) are tree pairs, then there is a tree pair \(R\) such that \(f_Pf_Q=f_R\). 
\end{lemma}
\begin{proof}
    \luna{todo prove}
\end{proof}
\begin{lemma}\label{lem:V_has_inverses}
\uses{def:tree_pair_to_prefix_replacement}
    If \(P\) is a tree pair, then \(f_P\) is a bijection and there is a tree pair \(Q\) such that \(f_P^{-1}=f_Q\).
\end{lemma}
\begin{proof}
    \luna{todo prove}
\end{proof}

\begin{definition}\label{def:V_cantor}
\uses{lem:V_is_semigroup, def:tree_pair_to_prefix_replacement}
    We define \(V_{cantor}\) to be the set of functions \(\makeset{f_{P}}{\(P\) is a tree pair}\). We give this set the binary operation of composition of functions and the unary operation of inversion.
    These operations are well-defined by Lemma~\ref{lem:V_is_semigroup} and Lemma~\ref{def:tree_pair_to_prefix_replacement}.
\end{definition}
\begin{definition}\label{def:V_tree_pair}
    We define \(V_{tree}\) to be the set of \(\sim\) equivalence classes of finite rooted binary trees.
    We define a binary operations on this set by \([P]_{\sim}[Q]_{\sim}=[R]_{\sim}\) if \(f_Pf_Q=f_R\) and a unary operation by \([P]_{\sim}^{-1}=[Q]_{\sim}\) if \(f_P^{-1}=f_Q\).
    These operations are well-defined by Definition~\ref{def:V_cantor} and Theorem~\ref{thm:Vtree_Vcant_bijection}.
\end{definition}
\section{Jonsson-Tarski Algebra Perspective}

\luna{I probably shouldn't be constantly conflating an algebra with its underlying set but I don't know the standard ways of handling such situations in rocq so for now I will do this anyway}
\begin{definition}\label{def:Jonsson-Tarski_Algebra}
    A Jonsson-Tarski Algebra is a 4-tuple \((A,\lambda,\alpha_0,\alpha_1)\) such that \(A\) is a set, \(\lambda\) is a binary operation on \(A\), \(\alpha_0, \alpha_1\) are unary operations on \(A\) and the following hold for all \(x,y\in A\):
    \[(x\alpha_0, x\alpha_1)\lambda = x, \quad (x,y)\lambda\alpha_0=x \quad \text{ and }\quad(x,y)\lambda\alpha_1=y.\]
\end{definition}
\begin{definition}\label{def:jt_homomorphism}
\uses{def:Jonsson-Tarski_Algebra}
    If \(A\) and \(B\) are Jonsson-Tarski algebras and \(\phi:A\to B\) is a function, then we say that \(\phi\) is a \emph{homomorphism} if for all \(x,y\in A \) we have
    \[(x)\phi\alpha_0=(x\alpha_0)\phi, \quad (x)\phi\alpha_1=(x\alpha_1), \quad \text{ and }\quad (x\phi,y\phi )\lambda= (x,y)\lambda \phi.\]
    \luna{maybe homomorphisms and isomorphisms are already defined in some general sense in preexisting packages}
\end{definition}
\begin{definition}\label{def:free_basis_jt}
\uses{def:jt_homomorphism}
If \(A\) is a Jonsson-Tarski algebra and \(X\subseteq A\), then we say that \(X\) is a \emph{free-basis} for \(A\) if for all Jonsson-Tarski algebras \(B\) and functions \(\phi:X\to B\), there is a unique homomorphism \(\tilde{\phi}:A \to B\) such that \((x)\tilde{\phi}=(x)\phi\) for all \(x\in X\).
\end{definition}

\begin{definition}\label{def:jt_expression}
\rocq{Thompson.codes.jt_expression}

A \emph{Jonsson-Tarski expression} is either
\begin{itemize}
    \item The empty expression;
    \item \(\text{Left}\ E\) where \(E\) is a Jonsson-Tarski expression;
    \item \(\text{Right}\ E\) where \(E\) is a Jonsson-Tarski expression;
    \item \(\text{Node}\ L\ R\) where \(E\) is a Jonsson-Tarski expression.
\end{itemize}
\end{definition}

\begin{definition}\label{def:reduced_jt_expression}
A \emph{reduced Jonsson-Tarski expression} is either
\begin{itemize}
    \item The empty expression;
    \item \(\text{Left}\ E\) where \(E\) is a Jonsson-Tarski expression not of the form $\text{Node}\ L\ R$;
    \item \(\text{Right}\ E\) where \(E\) is a Jonsson-Tarski expression not of the form $\text{Node}\ L\ R$;
    \item \(\text{Node}\ L\ R\) where there is no Jonsson-Tarski expression \(E\) with \(L= \text{Left}\ E\) and \(R= \text{Right}\ E\).
\end{itemize}
\end{definition}
\begin{lemma}\label{lem:free-jt-algebra}
    \uses{def:jt_expression}
    The family of reduced Jonsson-Tarski expressions with the obvious operations form a Jonsson Tarski algebra \(\mathcal{J}\).
\end{lemma}
    \begin{proof}
        \luna{todo prove}
    \end{proof}
\begin{lemma}\label{lem:freejt_is_free}
\uses{lem:free-jt-algebra}
    The algebra \(\mathcal{J}\)from Lemma~\ref{lem:free-jt-algebra} is freely generated by the empty expression.
\end{lemma}

\begin{definition}\label{def:V_jonsson_tarski}
\uses{lem:freejt_is_free}
    The group \(V_{jt}\) is the automorphism group of \(\mathcal{J}\).
\end{definition}


\chapter{Thompsons groups and monoids}

\chapter{Presentations}
